Self Regulation Ontology Retest Data Report

### 2017-11-30 code/SRO_Report.Rmd
misc

```{r warning=FALSE, message=FALSE}
workers = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/Local/User_717570_workers.csv')
workers = workers %>% 
  group_by(Worker.ID) %>%
  mutate(Retest_worker=ifelse(sum(CURRENT.RetestWorker,CURRENT.RetestWorkerB2,CURRENT.RetestWorkerB3,CURRENT.RetestWorkerB4,CURRENT.RetestWorkerB5,na.rm=T)>0,1,0)) %>%
  ungroup()

worker_counts <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/Local/retest_worker_counts.json')

@@

```{r warning=FALSE, message=FALSE}
disc_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/Local/discovery_completion_dates.csv', header=FALSE)
val_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/Local/validation_completion_dates.csv', header=FALSE)
test_comp_date = rbind(disc_comp_date, val_comp_date)
rm(disc_comp_date, val_comp_date)
retest_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/Local/retest_completion_dates.csv', header=FALSE)
comp_dates = merge(retest_comp_date, test_comp_date, by="V1")
names(comp_dates) <- c("sub_id", "retest_comp", "test_comp")
comp_dates$retest_comp = as.Date(comp_dates$retest_comp)
comp_dates$test_comp = as.Date(comp_dates$test_comp)
comp_dates$days_btw = with(comp_dates, retest_comp-test_comp)
```

@@

```{r}
test_demog <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/t1_data/demographic_health.csv')

retest_demog <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_09-27-2017/demographic_health.csv')

@@

```{r echo=FALSE}
#Get variables of interest from Ian's release
tmp1 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_10-08-2017/meaningful_variables.csv')
tmp2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_10-08-2017/meaningful_variables_noDDM.csv')
tmp3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_10-08-2017/meaningful_variables_EZ.csv')
retest_report_vars = c(names(tmp1), names(tmp2), names(tmp3))
retest_report_vars = unique(retest_report_vars)
lit_rev_vars = as.character(unique(lit_review$dv)[which(unique(lit_review$dv) %in% retest_report_vars == FALSE)])
retest_report_vars = c(retest_report_vars, lit_rev_vars)
rm(tmp1, tmp2, tmp3, lit_rev_vars)
```

@@

for(i in 1:length(numeric_cols)){
  rel_df[numeric_cols[i], 'spearman'] <- get_spearman(numeric_cols[i]) 
  rel_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i])
  rel_df[numeric_cols[i], 'pearson'] <- get_pearson(numeric_cols[i])
  rel_df[numeric_cols[i], 'eta_sq'] <- get_eta(numeric_cols[i])
  rel_df[numeric_cols[i], 'sem'] <- get_sem(numeric_cols[i])
  rel_df[numeric_cols[i], 'var_subs'] <- get_var_breakdown(numeric_cols[i])$subs
  rel_df[numeric_cols[i], 'var_ind'] <- get_var_breakdown(numeric_cols[i])$ind
  rel_df[numeric_cols[i], 'var_resid'] <- get_var_breakdown(numeric_cols[i])$resid
}

>>>>

```{r warning=FALSE, message=FALSE}
workers = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/User_717570_workers.csv')
workers = workers %>% 
  group_by(Worker.ID) %>%
  mutate(Retest_worker=ifelse(sum(CURRENT.RetestWorker,CURRENT.RetestWorkerB2,CURRENT.RetestWorkerB3,CURRENT.RetestWorkerB4,CURRENT.RetestWorkerB5,na.rm=T)>0,1,0)) %>%
  ungroup()

worker_counts <- fromJSON('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/retest_worker_counts.json')

@@

```{r warning=FALSE, message=FALSE}
disc_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/discovery_completion_dates.csv', header=FALSE)
val_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/validation_completion_dates.csv', header=FALSE)
test_comp_date = rbind(disc_comp_date, val_comp_date)
rm(disc_comp_date, val_comp_date)
retest_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/Local/retest_completion_dates.csv', header=FALSE)
comp_dates = merge(retest_comp_date, test_comp_date, by="V1")
names(comp_dates) <- c("sub_id", "retest_comp", "test_comp")
comp_dates$retest_comp = as.Date(comp_dates$retest_comp)
comp_dates$test_comp = as.Date(comp_dates$test_comp)
comp_dates$days_btw = with(comp_dates, retest_comp-test_comp)
```

@@

```{r}
test_demog <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/t1_data/demographic_health.csv')

retest_demog <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_11-27-2017/demographic_health.csv')

@@

```{r echo=FALSE}
#Get variables of interest from Ian's release
tmp1 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_11-22-2017/meaningful_variables.csv')
tmp2 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_11-22-2017/meaningful_variables_noDDM.csv')
tmp3 <- read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_11-22-2017/meaningful_variables_EZ.csv')
retest_report_vars = c(names(tmp1), names(tmp2), names(tmp3))
retest_report_vars = unique(retest_report_vars)
lit_rev_vars = as.character(unique(lit_review$dv)[which(unique(lit_review$dv) %in% retest_report_vars == FALSE)])
retest_report_vars = c(retest_report_vars, lit_rev_vars)
rm(tmp1, tmp2, tmp3, lit_rev_vars)
```

@@

for(i in 1:length(numeric_cols)){
  rel_df[numeric_cols[i], 'spearman'] <- get_spearman(numeric_cols[i]) 
  rel_df[numeric_cols[i], 'icc'] <- get_icc(numeric_cols[i])
  rel_df[numeric_cols[i], 'pearson'] <- get_pearson(numeric_cols[i])
  rel_df[numeric_cols[i], 'partial_eta_sq'] <- get_partial_eta(numeric_cols[i])
  rel_df[numeric_cols[i], 'sem'] <- get_sem(numeric_cols[i])
  rel_df[numeric_cols[i], 'var_subs'] <- get_var_breakdown(numeric_cols[i])$subs
  rel_df[numeric_cols[i], 'var_ind'] <- get_var_breakdown(numeric_cols[i])$ind
  rel_df[numeric_cols[i], 'var_resid'] <- get_var_breakdown(numeric_cols[i])$resid
}
